\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-18 paper/main.tex
.

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two types
of features: structural information for drugs and proteins that can be
used to determine if the drug and protein physically interact, and
information about phenotypic effects of drugs and changes in protein
function that may ``localize'' on an interaction network (i.e.,
neighboring nodes will share some of these features or be
phenotypically similar).  As structural features, \name uses
structural representations of drugs from the SMILES transformer
\cite{SmilesTransformer} and representations of protein amino acid
sequences from DeepGOPlus \cite{DeepGoPlus}.  \name learns
representations of drug effects and protein functions using the
ontology-based machine learning method DL2Vec \cite{DL2vec2020} and
ontology-based annotations of drugs and proteins.

>>>>

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two types
of features: structural information for drugs and proteins that can be
used to determine if the drug and protein physically interact, and
information about phenotypic effects of drugs and changes in protein
function that may ``localize'' on an interaction network (i.e.,
neighboring nodes will share some of these features or are
phenotypically similar).  As structural features, \name uses
structural representations of drugs from the SMILES transformer
\cite{SmilesTransformer} and representations of protein amino acid
sequences from DeepGOPlus \cite{DeepGoPlus}.  \name learns
representations of drug effects and protein functions using the
ontology-based machine learning method DL2Vec \cite{DL2vec2020} and
ontology-based annotations of drugs and proteins.
